Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-08-24 TitlePage.tex
Revise titlepage layout
* Ensure it gets the right pagestyle
* Move \cleardoublepage to the scope of the empty pagestyle, so that the
  produced pages use it.
* Use `\vspace[*]` and `\stretch` (that is, `fill`) carefully, instead of other
  mixed vertical skips.
* Increase title `\linespread` to 1.3.

T\"ubingen\\
2017

@@

% 3 bigskips in a row.
% https://tex.stackexchange.com/a/245663/1340
\vspace{\dimexpr \bigskipamount * 3 \relax}
%
% https://tex.stackexchange.com/a/16261/1340
\begin{tabular}{@{}ll@{}}
Tag der mündlichen Qualifikation: & tt.mm.2017\\
Dekan:               & Prof.\ Dr.\ Wolfgang Rosenstiel\\
1.\ Berichterstatter: & Prof.\ Dr.\ Klaus Ostermann\\
2.\ Berichterstatter: & Prof.\ Dr.\ Fritz Henglein
\end{tabular}
%
\vspace{-1cm} %XXX revise when changing geometry.
%
%
\cleardoublepage
{% Group with normal linespread
\linespread{1}
\selectfont
\begin{flushright}
  \vspace*{\stretch{1}}
  To the memory of my mother Rosalia\\
  ~\\
  Alla memoria di mia madre Rosalia

>>>>

T\"ubingen\\
2018

@@

% 3 bigskips in a row.
% https://tex.stackexchange.com/a/245663/1340
\vspace{\dimexpr \bigskipamount * 3 \relax}
%
% https://tex.stackexchange.com/a/16261/1340
\begin{tabular}{@{}ll@{}}
Tag der mündlichen Qualifikation: & 26.01.2018\\
Dekan:               & Prof.\ Dr.\ Wolfgang Rosenstiel\\
1.\ Berichterstatter: & Prof.\ Dr.\ Klaus Ostermann\\
2.\ Berichterstatter: & Prof.\ Dr.\ Fritz Henglein
\end{tabular}
%
\vspace{-1cm} %XXX revise when changing geometry.
%
%
\cleardoublepage
{% Group with normal linespread
\linespread{1}
\selectfont
\begin{flushright}
  \vspace*{\stretch{1}}
  To the memory of my mother Rosalia (1946--2016)\\
  ~\\
  Alla memoria di mia madre Rosalia (1946--2016)
